

I first want to thank my supervisor, Teppei Katori. I think he got
close to the what I consider is the best out of me over these three
years. I learnt a lot in neutrino physics, but also in other related
fields, such as neutrino cross sections, detector physics, exotic
neutrino physics, ``politics physics,'' a bit of ``gossip physics,''
and ``Ig physics.'' I think all of these are very valuable for the
future, and I certainly enjoyed learning all this and doing my
PhD. Thank you Teppei for your support.

I also want to thank Francesca Di Lodovico, who gave me the
opportunity to ``have a go'' in Queen Mary, University of London, over
a long internship and try a mini-analysis, just before my PhD
started. This conforted me in my choice for making a PhD here.

I am greateful to my fellow PhDs, Sophie (at the time), Nick, Paul,
Tom, Andres, Shivesh, Eddie, Rodrigo, Thomas and Susanna. Thank you
Queen Mary post docs and staff, Ryan, Sam, Sophie (again), St\'ephane
and Alex. Thank you all for your friendly support, advice, and of
course the litres of beers, pubs and pool we have shared. Good luck
for the ones who still have to graduate!

Thank you T2K UK students and post docs, Clarence, Raj, Callum,
Patrick, Luke, Steve, Dave, Jon and Leon for showing me around in
Tokai, for the ski in Mioko, and for the fun during Shin Shan and Pono
Pono evenings.

Thanks Clarence, Callum and Patrick for the help with Nuisance.

Merci Simon pour les derniers plots de la th\`ese!

Thanks Jos\'e, Xiaoyue, Ko, Yano-san for making SK shifts less boring.

Finally, thank you Jigmet, for your patience and perseverance, across
the seas. Thanks for making the trip to London and France several
times, and for the nice time during the layovers on the way to
Japan. Thanks for sometimes reminding me how ``{\it pagal}'' this all
has been, and thanks for pulling me out of work when it was too much,
and taking me out. Thanks for letting me chopping the onions and
veggies in your sacred sanctuary, the kitchen.

Merci Eliot, pour l'inconditionnel support, les cheeky bi\`eres du
soir en rentrant du labo, la musique, l'appartement et les petites
tueries de p\^atisseries.

Merci papa, maman pour votre support et encouragements, par Skype, par
t\'el\'ephone, sur un v\'elo ou sur les chemins boueux
pyr\'en\'eens.

Merci Natacha d'avoir eu la patience de relire enti\`erement cette
th\`ese!

Merci Alexis de m'avoir fait refaire de l'escalade!

Merci aux copains fran\c{c}ais, Olivier, Vivien, Claire,
Pierre, Sarah, Quentin, Youmna pour les weekends et escapades, et
surtout pour vos patiences; je n'ai pas \'et\'e souvent en France
pendant la th\`ese, j'en suis d\'esol\'e.

Thanks ``F*ckoffee'' (excuse my French), in Bermondsey, for the long
afternoons spend behind my laptop and double espressos.

\newpage
\vspace*{\fill}
\begin{adjustbox}{right}
  \begin{it}
    To those who endure the ones doing a PhD.
  \end{it}
\end{adjustbox}
\vspace*{\fill}
