
Neutrinos were postulated in 1930 by W. Pauli to explain missing
energy in the beta decays of nitrogen and lithium, in a famous letter
to the ``{\it radioactive ladies and gentlemen}~\cite{Pauli1930}.''
At the time, postulating a new, undetected, particle was quite
controversial; it is now considered a breakthrough. These particles
were later experimentally discovered by Reines and Cowan in
1953~\cite{Reines1953}. They measured the inverse beta decays,
$\bar{\nu}_e+p\rightarrow e^++n$, initiated by the Savannah nuclear
reactor anti-neutrinos on cadmium-doped water.

Since then, the observation of neutrinos is still a challenge for
physicists, but there are a wide number of experiments that observe
neutrinos from very different
sources~\cite{T2K2011,SK2003,SNO2000,DayaBay2015}, such as the Sun,
cosmic ray interacting with the atmosphere, nuclear reactors or
accelerated protons impinging a target.

This section is dedicated to the description of neutrino properties;
the first section of this chapter describes the oscillatory behaviour
of the neutrinos. Precise and reliable measurements of this phenomenon
are the main purpose of the \Gls{TK} experiment~\cite{T2K2011}, which
measures muon electron (anti-) neutrinos appearance in a muon (anti-)
neutrino beam of 600~MeV, in Japan\footnote{Muon (anti-) neutrinos of
  energy 600~MeV are created at Tokai in the \Gls{JPARC} facility. The
  Super-Kamiokande detector (\Gls{SK}), in Kamioka (295~km away)
  detects the oscillated neutrino signal. The Near Detector (\Gls{ND})
  at 280~m, in Tokai of this experiment is used for the analyses
  develeped in this thesis.}.

The second section of this chapter is about the phenomenology of
neutrino cross sections. This is a fundamental input to the
oscillation measurements made at \Gls{TK} and the subject of this
thesis. The section will only cover the ``mid-range'' energies (0.5 to
few GeV) cross sections, which are relevant to in the \Gls{TK}
case. The section starts with a common description of the processes
that happen when a neutrino interacts with matter, with an emphasis on
the measurements within and outside of \Gls{TK} that are the most
sensitive to these channels.

\section{Oscillation physics}
\label{sec:oscillation}
\input{Oscillation.tex}

\section{Medium energy neutrino scattering physics}
\label{sec:crosssection}
\input{CrossSection.tex}
